Supporting Information: Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications

### 2021-09-30 vertical-thermal-review_SI.Rmd
just upload fig_6.jpg that Elsa sent, and suggested edits doc from Elsa into the archive to review

Digital terrain models (DTMs) were created for each plot using minimum quantile spline regression and interpolation (see Shao et al. 2019) and used to normalize the voxelized lidar data with respect to the ground height. Leaf area density (LAD, $m^2$ $m^-3$) was estimated by applying the MacArthur-Horn transformation [@macarthurFoliageProfileVertical1969] to the voxelized pulse returns. We excluded LAD data at the bottom 5 m of the canopy, which are more uncertain due to limited pulse penetration within this region furthest away from the sensor [@starkAmazonForestCarbon2012]; for calibration purposes, we assumed the bottom 5 m to have a leaf area index (LAI) of 0.25 $m^2$ $m^{-2}$ [@shaoHighThroughputAssessment2019].

>>>>

Digital terrain models (DTMs) were created for each plot using minimum quantile spline regression and interpolation (see Shao et al. 2019) and used to normalize the voxelized lidar data with respect to the ground height. Leaf area density (LAD, $m^2$ $m^{-3}$) was estimated by applying the MacArthur-Horn transformation [@macarthurFoliageProfileVertical1969] to the voxelized pulse returns. We excluded LAD data at the bottom 5 m of the canopy, which are more uncertain due to limited pulse penetration within this region furthest away from the sensor [@starkAmazonForestCarbon2012]; for calibration purposes, we assumed the bottom 5 m to have a leaf area index (LAI) of 0.25 $m^2$ $m^{-2}$ [@shaoHighThroughputAssessment2019].
